### 2021-12-15 documentos/pce.tex
dandole

where $\tau_k$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},

@@

where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.

@@

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec k}$ either $1$ or $0$.
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper. Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.

>>>>

where $\tau_\alpha$ is either $1$ or $0$. It is well-known that not every operation like this is a quantum map, for example collapsing the entire Bloch ball into a disk of radio equal to one is not a quantum channel. A direct evaluation of the complete positivity conditions~\cite{zimansbook,davalosdivisibility},

@@

where trace-preserving is already imposed ($\tau_0=1$), show that only five operations are \pce: the identity map, the completely depolarizing channel ($\rho \mapsto \one/2$); and completely bit, phase, and the bit-phase flip channels~\cite{chuangbook}. These operations are by definition diagonal in the Pauli basis~\cite{Ziman2005,davalosdivisibility}, \ie{} $\hat \mcE=\diag{\left(1,\tau_x, \tau_y, \tau_z \right)}$, and can be pictured using one column tables showing the positions of $1$s and $0$s in the diagonal of the channel (in the Pauli basis), see~\fref{fig:one:qubit:examples}.

@@

As mentioned above, \pce{} maps nullify Pauli strings, thus, consider the linear operations acting in the generalized Bloch vector $\vec r_{\vec \alpha}$,
\begin{equation}
	\paulicomponents \mapsto \taus \paulicomponents.
% 	\taus = 0,1, \hspace{1.5cm}	\tau_{0,\ldots,0}=1,
\label{eq:definition:Pauli}
\end{equation}
with $\tau_{\vec \alpha}$ either $1$ or $0$.
Similar to the qubit case, not every operation with this form is a \cptp{} map. For the operation to be trace preserving, it is easy to prove that $\tau_{\vec 0}=1$. On the other hand, constructing and evaluating the conditions for complete positivity is involved and is the main problem addressed in this paper. Moreover, these operations are by definition diagonal in the $\left\{ 2^{-N/2}\sigma_{\vec
\alpha} \right\}$ basis.
